|

### 2018-11-27 Paper.Rmd
stuff

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
suppressMessages(library("tidyverse")) # everything 
library(plm) # For linear panel regression
library(stargazer) # For regression outputs #fail 
library(texreg) # For regression outputs #fail 
library(kableExtra) # For regression outputs 
library(broom) # Because Matt Worthington said so 
library(knitr) # Because Matt Worthington said so

@@

@@

##Design and Data 
<!--Add in summary statistics?-->
In this paper, I build upon the growing body of state-level political science research to ask whether campaign contribution limits at the state level associated with lower levels of corruption. Given open debate about the proper measure of state-level corruption, I use two measures. The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data. The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016). I combine these measures with a third data set from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth data set from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012). 
Barber’s data set is a panel of contribution limits from 1990-2012 for the lower house of every state legislature. Barber compiled this data set from the FEC, Westlaw, and the Nation Council of State Legislatures. Each dollar amount is inflation indexed to 2010 dollar amounts, and bi-annualized. There are three different types of limits in the Barber database: Individual contribution limits, individual-to-party limits, and PAC limits. Barber utilized individual and PAC contributions in his analysis of polarization, leaving out individual-to-party limits given that party contributions typically make up less than 10% of total political fundraising; I include it this analysis to determine whether parties, rather than PACs or individuals, might be the locus of corruption as measured by our other two data sets (Barber 2016).

@@

If the model above fails to show an initial correlation, this may be due to the confounding effect of absent variables. In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above. These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization. Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, can better identify the association of campaign finance laws with corruption levels.

### Model II: Difference-in-Difference Model
<!--Add specification, formulas?-->
Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, could be correlated with decreases in corruption. A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant. If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.

@@

The second set of models (Table II) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.10 point decline in the Corruption Reflection Index. The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), meaning that the presence of individual-to-party limits is associated with a 10% decrease in the index.

>>>>

```{r setup, include=FALSE}
# This is all necessary setup stuff, including packages and for Markdown
knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
suppressMessages(library("tidyverse")) # everything 
library(plm) # For linear panel regression
library(stargazer) # For regression outputs #fail 
library(texreg) # For regression outputs #fail 
library(kableExtra) # For regression outputs 
library(broom) # Because Matt Worthington said so 
library(knitr) # Because Matt Worthington said so

@@

```{r panel effects modeling, eval=F}
# Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf
# On robust standard errors https://stats.stackexchange.com/questions/117052/replicating-statas-robust-option-in-r
# And https://cran.r-project.org/web/packages/sandwich/vignettes/sandwich.pdf
# And https://www.brodrigues.co/blog/2018-07-08-rob_stderr/, 
# Pretty good explanation here https://www.methodsconsultants.com/tutorial/introduction-to-random-effects-models-including-hlm/
# Go through this? https://github.com/tyleransom/EconometricsLabs/blob/master/tidyRcheatsheet.pdf
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")
```

@@

##Design and Data 
<!--Add in summary statistics?-->
In this paper, I build upon the growing body of state-level political science research to ask whether campaign contribution limits at the state level associated with lower levels of corruption. Given open debate about the proper measure of state-level corruption, I use two measures. The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data. The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016). I combine these measures with a third data set from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth data set from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).

Barber’s data set is a panel of contribution limits from 1990-2012 for the lower house of every state legislature. Barber compiled this data set from the FEC, Westlaw, and the Nation Council of State Legislatures. Each dollar amount is inflation indexed to 2010 dollar amounts, and bi-annualized. There are three different types of limits in the Barber database: Individual contribution limits, individual-to-party limits, and PAC limits. Barber utilized individual and PAC contributions in his analysis of polarization, leaving out individual-to-party limits given that party contributions typically make up less than 10% of total political fundraising; I include it this analysis to determine whether parties, rather than PACs or individuals, might be the locus of corruption as measured by our other two data sets (Barber 2016).

@@

As demonstrated below, this model fails to uncover any initial correlation between changes in campaign finance law and CCI or CRI scores. This may be due to the confounding effect of absent variables. In order to test that, I build a model of political corruption using control variables previously demonstrated to be correlated with corruption arrests, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above. These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization. Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, can better identify the association of campaign finance laws with corruption levels.

### Model II: Difference-in-Difference Model
<!--Add specification, formulas?-->
Even if the panel models above fail to capture correlation between state level campaign finance laws and corruption arrests, it could be the case that changes in campaign finance laws, rather than relative campaign finance limits, are correlated with decreases in corruption. A difference-in-difference regression can help identify this by comparing the state-years in which campaign finance laws changed to state-years where they remained constant. If tighter campaign finance laws are correlated with lower corruption levels, then a change in one year should lead to lower corruption convictions in the years following.

@@

The second set of models (Table II) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.10 point decline in the Corruption Reflection Index. The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 10% decrease in the index.
